---
title: "Data-Processing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data-Processing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pru3di)
```

This vignette shows how to read in the source data and process it to generate the milestone table for each valid trajectory.

# Overview

The 3Di algorithm defines a composite "(in)efficiency" score for each flight.
The score is composed of a horizontal and vertical component.

# Data Loading and Processing

Let's load a subset of trajectories.

```{r}
rq <- eidw_egll |> 
  standardise_traj_from_trafficlib() |> 
  identify_trajectory_legs() |> 
  make_uid()

dplyr::glimpse(rq)
```

Let's pick a random set of trajectories and plot them.

```{r}
set.seed(666)
picks <- rq$UID |> unique() |> sample(3)
picks
```

```{r}
library(ggplot2)

rq |> dplyr::filter(UID %in% picks) |> 
  ggplot() +
  geom_point(aes(x = TIME, y = FL, color = FLTID)) +
  theme(legend.position = "top")
```


# Horizontal Component

calc the horiz comp

# Vertical Component

# Construct Score
